IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-29 ms.tex
I added more details about the flat fielding and background subtraction.

For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.

@@

>>>>

For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
We obtained spectrophotometry over 4.65 hours, covering about half of a rotation period for 2MASS J0835.

@@

For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.
For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.

As in \citep{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
